---
title: "Modelling Competition: House Prices"
author: 
- Roberto Alvarez Llordachs
- Javier Goñi Artieda
- Marcos Crespo Díaz
- Gabriela Levenfeld Sabau
- Sofía Gianelli Nan
- Miguel Díaz-Plaza Cabrera
date: "`r Sys.Date()`"
output:
  pdf_document: 
    toc: yes
    toc_depth: 4
    number_sections: yes
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

House prices have sparked lot of debate recently in our society. Currently, this topic has aroused controversy on the grounds that has been a cornerstone in 2008 crisis. Were buyers to decide a model for setting the selling price, which factors would be included and what would be their weight?

The goal of this project is to create a effective price prediction model.




# Data Preparation

First step would be to load both databases, train and test.
```{r}
train <- read.csv("train.csv", sep=",")
test <- read.csv("test.csv", sep=",")

column_diff <- setdiff(names(train), names(test))
```
We can see that train contain one more column than test, this extra column is `r column_diff`.
The data set collects 2919 observations of different features of residential houses in Ames, Iowa. The number of features is given by the number of columns 



Ideas en base a Lab1:

- Data preprocessing: Remove unnecesary columns such as ID, in Lab1 remove characteristics with one observation. Check that categorical variables are factors. Check summary to check everything is correct.

- After datapreprocessing do Exploratory analysis: Correlations (ggpairs, in Lab 2 values and colors), histograms of predictors, plots of response vs some predictors (only comment important ones)

- Modeling: regsubsets only when continuous, Lab1 use stepAIC... Check model assumptions.

- Prediction


